Gozde and Liora Replication Code

### 2015-05-11 replication only.Rmd
Wrote function for graphs

# Preparing data for analysis
#lines 62-83 of this code are based on (though not identical to) the code written by Harvardstudents in their previous replication of this paper.  Citation : Noam Gidron; Jeffrey Javed, 2011, "Replication data for: The Unholy Trinity: Immigration, Unemployment and Extremism in Europe, 1980-2002", http://hdl.handle.net/1902.1/15902 V1 [Version]

@@

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
library(msm)
asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01) # vector with possible values for asylumseekers

@@

# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

# Creating the first graph with ggplot

variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Asylumseekers"
ytitle <- "Effect: Unemployment"
main <- "Figure 1: The Conditional Effects of Unemployment and Immigration"
graph_1 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") +
  labs(x = xtitle, y = ytitle, title = main) +
  coord_fixed(ratio = 8)

@@

unemployment <- seq(from = min(data$z_unemp), to = max(data$z_unemp), by = .01) # vector with possible values for unemployment
variable <- unemployment # standardized label
slopes <- model$coef$fixed["z_asylumseeker"] + model$coef$fixed["z_asylumseeker:z_unemp"] * variable # Estimated slopes based on estimated coefficients of asylumseekers (16) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

# Creating the second graph with ggplot:

variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Unemployment"
ytitle <- "Effect: Asylum seekers"
main <- "The Conditional Effects of Unemployment and Immigration"
graph_2 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") +
  labs(x = xtitle, y = ytitle) +
  coord_fixed(ratio = 12)

@@

# Figure 2, graph 1
salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
variable <- salience
slopes <- model$coef$fixed["var_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
variable.data <- cbind(variable, slopes, upper, lower)

# Creating the first graph with ggplot:

variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Salience"
ytitle <- "Effect: Variance"
main <- "The Conditional Effects of Salience and Variance"
graph_3 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") +
  labs(x = xtitle, y = ytitle, title = main) +
  coord_fixed(ratio = 400)

# Second part of Figure 2:

variance <- seq(from = min(data$var_c), to = max(data$var_c), by=10) # vector with possible values for variance
variable <- variance
slopes <- model$coef$fixed["salience_mean_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors

for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)

# Creating the second graph with ggplot:

variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Variance"
ytitle <- "Effect: Salience"
main <- "The Conditional Effects of Salience and Variance"
graph_4 <- ggplot(variable.data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + 
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") +
  labs(x = xtitle, y = ytitle, title = main) +
  coord_fixed(ratio = 500)

>>>>

# Preparing data for analysis
#lines 64-83 of this code are based on (though not identical to) the code written by Harvard students in their previous replication of this paper.  Citation : Noam Gidron; Jeffrey Javed, 2011, "Replication data for: The Unholy Trinity: Immigration, Unemployment and Extremism in Europe, 1980-2002", http://hdl.handle.net/1902.1/15902 V1 [Version]

@@

# Figure 1 (Conditonal Effects of Unemployment and Immigration)
![Figure 1](figures/fig1.png)
```{r}
library(msm) #includes deltamethod function, which allows us to obtain standard errors of transformed parameters
#Function with which we will create each graph
graph <- function(data, ratio, ymin, ymax) {
  ggplot(data, aes(x = variable, y = slopes)) + 
  geom_line(aes(y = slopes), color = "blue") + #color will always be blue
  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = 0.2) + 
  geom_hline(yintercept = 0, size = 0.4, color = "black") + #fixed y intercept and color
  labs(x = xtitle, y = ytitle, title = main) + #titles will call from prepared data
  coord_fixed(ratio)
}
#Preparing the data for the first graph
asy <- seq(from = min(data$z_asylumseeker), to = max(data$z_asylumseeker), by = .01) # vector with possible values for asylumseekers

@@

# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)
variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Asylumseekers"
ytitle <- "Effect: Unemployment"
main <- "Figure 1: The Conditional Effects of Unemployment and Immigration"

#creating the first graph using our ggplot function
graph_1 <- graph(data = variable.data, ratio = 8)
graph_1

@@

#Preparing the data for the second graph
unemployment <- seq(from = min(data$z_unemp), to = max(data$z_unemp), by = .01) # vector with possible values for unemployment
variable <- unemployment # standardized label
slopes <- model$coef$fixed["z_asylumseeker"] + model$coef$fixed["z_asylumseeker:z_unemp"] * variable # Estimated slopes based on estimated coefficients of asylumseekers (16) and unemployment x immigration (36)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x16) + (x36) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)
variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Unemployment"
ytitle <- "Effect: Asylum seekers"
main <- "The Conditional Effects of Unemployment and Immigration"
#Creating the second graph with our function
graph_2 <- graph(data = variable.data, ratio = 12)
graph_2

@@

# Figure 2, graph 1
#Preparning the data to graph
salience <- seq(from = min(data$salience_mean_c), to = max(data$salience_mean_c), by=.1) # vector with possible values for salience
variable <- salience
slopes <- model$coef$fixed["var_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (21) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors
for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x21) + (x39)*j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
variable.data <- cbind(variable, slopes, upper, lower)
variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Salience"
ytitle <- "Effect: Variance"
main <- "The Conditional Effects of Salience and Variance"

#Creating the first graph with our function
graph_3 <- graph(data = variable.data, ratio = 400)
graph_3

# Second part of Figure 2:
#Preparing the data to graph
variance <- seq(from = min(data$var_c), to = max(data$var_c), by=10) # vector with possible values for variance
variable <- variance
slopes <- model$coef$fixed["salience_mean_c"] + model$coef$fixed["salience_mean_c:var_c"] * variable # Estimated slopes based on estimated coefficients of salience (20) and salience x variance (39)
estmean <- model$coef$fixed # Estimated means for variables 
estvar <- vcov(model) # Estimated covariances
se <- rep(NA, length(variable)) # Creating empty vector for predicted s.e. values
# Creating a loop with deltamethod to calculate estimated standard errors

for (i in 1:length(variable)) {
  j <- variable[i]
  se[i] <- deltamethod (~ (x20) + (x39) * j, estmean, estvar)
}
# Create confidence intervals and combine all values in matrix.
upper <- slopes + 1.96 * se
lower <- slopes - 1.96 * se
variable.data <- cbind(variable, slopes, upper, lower)
variable.data <- data.frame(variable.data) # Turn matrix into data frame so that ggplot can read it.
xtitle <- "Variance"
ytitle <- "Effect: Salience"
main <- "The Conditional Effects of Salience and Variance"

#Creating the second graph with our function
graph_4 <- graph(data = variable.data, ratio = 500)
graph_4
